### 2023-01-26 ms/ms.tex
fix abstract

The rules in cricket treat the competing teams asymmetrically, even before the start of physical play. In the one-day version of the game, for instance, which team bats first is determined by the captain that wins the toss. This raises questions about the effects of the asymmetry created by luck. Does the team that wins the toss have an advantage over the other team?

We find that, on average, the effect of winning the toss on winning the match is essentially nil in international limited-overs daytime matches but substantial (3.3 percentage points) in day/night matches. In test cricket, the advantage is even larger (4.9 percentage points). The advantage has exploded in the last decade (to nearly 15 percentage points) after a steady decline. More surprisingly, the effect of the toss does not appear to vary between competitive and noncompetitive pairings of teams. And as for the decision to bat or field first, we find the win-loss differential is significantly larger for the teams that elect to field than those that elect to bat, in which case it is negligible. Lastly, and perhaps most surprisingly, in rain-delayed matches in which the chasing team's total was adjusted by the Duckworth-Lewis formula, we find that teams that elected to bat first did just as well than those that elected to field first.

>>>>

In cricket, which team bats first is determined by a toss. Does the team that wins the toss have an advantage over the other team? We find that, on average, the effect of winning the toss on winning the match is essentially nil in international limited-overs daytime matches but substantial (3.3 percentage points) in day/night matches. In Test cricket, the advantage is even larger (4.9 percentage points). The advantage has exploded in the last decade (to nearly 15 percentage points) after a steady decline. Surprisingly, the effect of the toss does not appear to vary between competitive and non-competitive pairings of teams. And as for the decision to bat or field first, we find the win-loss differential is significantly larger for teams that elect to field; the advantage is negligible among those that elect to bat. Lastly, and perhaps most surprisingly, in rain-delayed matches in which the chasing team's total is adjusted by the Duckworth-Lewis formula, we find that teams that elected to bat first did just as well as those that elected to field first.
